### 2010-11-09 doc/manuals/janitor/tex_installation/installation.tex
implement option to enable/disable janitor

The current version of the Janitor can be configured using the
common file \textit{arc.conf}. It is expected in the configuration
directory \textit{etc}. The Janitor is using the environment
variable \textit{NORDUGRID\_CONFIG} to determine the location of the
corresponding file. If that variable is not set, the default location
\textit{/etc/arc.conf} will be used.  The configuration is assigned
by the section \lbrack janitor\rbrack. Table~\ref{tab:arcConfTags}
describes the available tags for the Janitor's configuration.

\begin{landscape}
\begin{table}[!h]
   \begin{center}
        \mycaption{Tags usable in \textit{arc.conf} within the section janitor.}{Tags usable in \textit{arc.conf} within the section janitor.}
	\label{tab:arcConfTags}
	\begin{longtable}{|p{3cm}|p{10cm}||p{10cm}|}
	\hline
	   \textbf{tag}    & \textbf{example}                      & \textbf{description}\\
        \hline
           enabled         & "1"                                   & Boolean flag which enables or disables janitor in A-REX.\\
	   uid             & "root"                                & The effective uid. \\
	   gid             & "0"                                   & The effective gid. \\
	   registrationdir & "/var/spool/nordugrid/janitor"        & Directory where we the current states of jobs are kept. \\
	   catalog         & "/var/spool/nordugrid/janitor/catalog/knowarc.rdf"& URL of the catalog containing the package information.\\
	   downloaddir     & "/var/spool/nordugrid/janitor/download" & Directory for downloads \\
	   installationdir & "/var/spool/nordugrid/janitor/runtime"& Directory for installation of packages                   \\
	   jobexpirytime   & "7200"                                & If a job is older than this, it is considered dead and assigned to be removal pending.\\
	   rteexpirytime   & "36"                                  & If a runtime environment was not used for this time, it will be assigned to be removal pending.\\
	   allow\_base     & "*"                                   & Allow rule for base packages. \\
	   deny\_base      & "debian::etch"                        & Deny rule for base packages.\\
	   allow\_rte      & "*"                                   & Allow rule for base packages. \\
	   deny\_rte       & "APPS/MATH/ELMER-5.0.2"               & Deny rule for base packages. \\
	   logconf         & "/opt/nordugrid/etc/log.conf"         & Location of the logging configuration file for janitor.\\
	\hline
	\end{longtable}
   \end{center}
\end{table}
\end{landscape}

The parameter \texttt{enabled} specifies whether the Janitor shall be used
within A-REX or not. This needs to be distinguished from the previously mentioned
compilation flags of a similar name. Use the value \texttt{"0"} to disable Janitor. The
\texttt{uid} and the \texttt{gid} are defining which effective user id
(uid) and group id (gid) shall be used for the Janitor.

>>>>

The current version of the Janitor can be configured using the
common file \textit{arc.conf}. It is expected in the configuration
directory \textit{etc}. The Janitor is using the environment
variable \textit{NORDUGRID\_CONFIG} to determine the location of the
corresponding file. If that variable is not set, the default location
\textit{/etc/arc.conf} will be used.  The parameter \texttt{use_janitor} in the
\lbrack grid-manager\rbrack section has to be set in order to tell A-REX
whether to use Janitor or not. By default, Janitor is not used. Use the value
\texttt{"1"} to enable Janitor.

Janitor is configured through parameters
in the section \lbrack janitor\rbrack. Table~\ref{tab:arcConfTags}
describes the available tags for the Janitor's configuration.

\begin{landscape}
\begin{table}[!h]
   \begin{center}
        \mycaption{Tags usable in \textit{arc.conf} within the section janitor.}{Tags usable in \textit{arc.conf} within the section janitor.}
	\label{tab:arcConfTags}
	\begin{longtable}{|p{3cm}|p{10cm}||p{10cm}|}
	\hline
	   \textbf{tag}    & \textbf{example}                      & \textbf{description}\\
        \hline
	   uid             & "root"                                & The effective uid. \\
	   gid             & "0"                                   & The effective gid. \\
	   registrationdir & "/var/spool/nordugrid/janitor"        & Directory where we the current states of jobs are kept. \\
	   catalog         & "/var/spool/nordugrid/janitor/catalog/knowarc.rdf"& URL of the catalog containing the package information.\\
	   downloaddir     & "/var/spool/nordugrid/janitor/download" & Directory for downloads \\
	   installationdir & "/var/spool/nordugrid/janitor/runtime"& Directory for installation of packages                   \\
	   jobexpirytime   & "7200"                                & If a job is older than this, it is considered dead and assigned to be removal pending.\\
	   rteexpirytime   & "36"                                  & If a runtime environment was not used for this time, it will be assigned to be removal pending.\\
	   allow\_base     & "*"                                   & Allow rule for base packages. \\
	   deny\_base      & "debian::etch"                        & Deny rule for base packages.\\
	   allow\_rte      & "*"                                   & Allow rule for base packages. \\
	   deny\_rte       & "APPS/MATH/ELMER-5.0.2"               & Deny rule for base packages. \\
	   logconf         & "/opt/nordugrid/etc/log.conf"         & Location of the logging configuration file for janitor.\\
	\hline
	\end{longtable}
   \end{center}
\end{table}
\end{landscape}

The \texttt{uid} and the \texttt{gid} are defining which effective user id
(uid) and group id (gid) shall be used for the Janitor.
